# Shiny Group Survey Results

```{r, echo=FALSE, message=FALSE, warning=FALSE}
dat<- read.csv(here::here("R _ RShiny  Survey (Responses) - Form Responses 1.csv"))
library(tidyverse)

dat2<-dat %>% 
  mutate(Branch = recode(Branch, 
                         "Population Biology Branch" = "PBB", 
                         "Population Dynamics Branch" = "PDB", 
                         "Cooperative Research" = "CRB", 
                         "Population Dynamics" = "PDB", 
                         "PopDy" = "PDB", 
                         "READ-EDAB" = "EDAB", 
                         "Protected Species Branch" = "PSB", 
                         "Habitat Ecology Branch" = "HEB", 
                         "Data and Information Systems" = "DIS FMRD", 
                         "READ/PDB" = "PDB", 
                         "Population dynamics" = "PDB", 
                         "Cooperative Research Branch" = "CRB", 
                         "Cooperative Research Branch " = "CRB",
                         "Social Sciences Branch " = "SSB", 
                         "Social Sciences Branch" = "SSB",
                         "Habitat Ecology" = "HEB", 
                         "DIS FMRD" = "DIS" 
                         )) %>% 
  rename("R_users" = "What.programming.software.do.you.use..and.how.often...R.", 
         "Py_users" = "What.programming.software.do.you.use..and.how.often...Python.", 
         "Mat_users" = "What.programming.software.do.you.use..and.how.often...Matlab.", 
         "IDL_users" = "What.programming.software.do.you.use..and.how.often...IDL.", 
         "SAS_users" = "What.programming.software.do.you.use..and.how.often...SAS." , 
         "Cpp_users" = "What.programming.software.do.you.use..and.how.often...C...", 
         "StatisticalAnalysis" = "In.what.capacity.do.you.use.R.as.a.part.of.your.work...Statistics.Data.Analysis.", 
         "Reporting" = "In.what.capacity.do.you.use.R.as.a.part.of.your.work...Reporting." , 
         "DataQAQC" = "In.what.capacity.do.you.use.R.as.a.part.of.your.work...Data.QA.QC." , 
         "Wrangling" = "In.what.capacity.do.you.use.R.as.a.part.of.your.work...Data.Wrangling.Manipulation.", 
         "Visualization" = "In.what.capacity.do.you.use.R.as.a.part.of.your.work...Data.Visualization." , 
         "Advanced_tools" = "Do.you.use.any.of.the.following.advanced.tools.in.RStudio.", 
         "N_shiny_users" = "Do.you.develop.Shiny.applications.in.R.or.are.you.interested.in.learning.more.about.Shiny.", 
         "Time_server_vs_local" = "How.much.time.do.you.spend.working.in.R.on.a.NEFSC.server.vs.working.on.your.local.machine.", 
         "shiny_obstacles" = "If.you.are.interested.in.creating.using.a.Shiny.app..but.haven.t.been.able.to.implement.one..what.challenges.are.you.facing..", 
         "Public_products" = "Do.you.have.projects.that.would.benefit.from.a.public.facing.Shiny.server." 
         
         
         )



```

These are the results from the shiny survey conducted June 2021. This survey asked folks from the Northeast Fisheries Science Center how they use R and Shiny for their work in the hopes to better understand common roadblocks and help to identify areas where we can further support the R and RShiny communities at the Center. 

This survey recieved `r length(unique(dat2$Name))` responses from `r length(unique(dat2$Branch))` branches. 


```{r,echo = FALSE, message = FALSE, warning=FALSE}


dat2 %>% dplyr::select(R_users, Py_users, Mat_users, IDL_users, SAS_users, Cpp_users) %>% 
  tidyr::pivot_longer(.,cols = c(R_users, Py_users,  Mat_users, IDL_users, SAS_users, Cpp_users), names_to = "Var", values_to = "Category") %>% 
  mutate(Value = c(1)) %>% 
  group_by(Var, Category) %>% 
  summarise(Value = sum(Value)) %>% 
  ungroup() %>% 
  mutate(Category = recode(Category, 
                           "This is the language I use the most" = "Most", 
                           "I sometimes use this, This is the language I use the most" = "Most",
                           "I sometimes use this" = "Sometimes",
                           "Maybe once or twice" = "Rarely",
                           "I don't use this" = "Never", 
                           "I don't use this, Maybe once or twice" = "Never")) %>% 
  filter(!Category == "", 
         !Category == "Never") %>% 
  mutate(Category = factor(Category, levels = c( "Rarely", "Sometimes","Most"))) %>% 
  ggplot2::ggplot()+
  ggplot2::geom_col(aes( y = Var, x = Value,  fill = Category))+
  ggplot2::ggtitle("Number of Software Users")+
  ggplot2::ylab(element_blank())+
  ggplot2::xlab("Number of Survey Participants")+
  ecodata::theme_ts()

```


```{r, echo = FALSE, message = FALSE, warning=FALSE}
dat2 %>% dplyr::select(StatisticalAnalysis, Reporting, DataQAQC, Wrangling, Visualization) %>% 
  tidyr::pivot_longer(.,cols = c(StatisticalAnalysis, Reporting, DataQAQC, Wrangling, Visualization), names_to = "Var", values_to = "Category") %>% 
  mutate(Value = c(1)) %>% 
  group_by(Var, Category) %>% 
  summarise(Value = sum(Value)) %>% 
  ungroup() %>% 
  #mutate(Category = recode(Category, 
                           # "This is the language I use the most" = "Most", 
                           # "I sometimes use this, This is the language I use the most" = "Most",
                           # "I sometimes use this" = "Sometimes",
                           # "Maybe once or twice" = "Rarely",
                           # "I don't use this" = "Never", 
                           # "I don't use this, Maybe once or twice" = "Never")) %>% 
  filter(!Category == "", 
         !Category == "Never", 
         !Category == "Not sure") %>% 
  mutate(Category = factor(Category, levels = c("I would if I knew how", "Occasionally", "Often","Regularly" ))) %>% 
  ggplot2::ggplot()+
  ggplot2::geom_col(aes( y = Var, x = Value,  fill = Category))+
  ggplot2::ggtitle("How are folks using R")+
  ggplot2::ylab(element_blank())+
  ggplot2::xlab("Number of Survey Participants")+
  ecodata::theme_ts()

```


```{r, echo = FALSE, message = FALSE, warning=FALSE}
dat4<- dat2 %>% 
  select(N_shiny_users) %>% 
    mutate(N_shiny_users = recode(N_shiny_users, 
                           "This is the language I use the most" = "Yes I am interested in learning more about Shiny apps", 
                           "I do not use, but have a general interest in it" = "Yes I am interested in learning more about Shiny apps",
                           "mildly interested - not sure I have a need for Shiny, but very open to it" = "Yes I am interested in learning more about Shiny apps",
                           "Unsure if I have a use for building Shiny Apps. I would have to learn more about it." = "Yes I am interested in learning more about Shiny apps",
                           "Yes I am interested in learning more about Shiny apps, Yes, I realize the value of Shiny apps. Any tips on switching from one language to another (I am a Stata user)?" = "Yes I am interested in learning more about Shiny apps", 
                           "Don't use it currently, but interested in how the center is using it" = "Yes I am interested in learning more about Shiny apps", 
                           "Yes I build Shiny apps, Yes I am interested in learning more about Shiny apps" = "Yes I am interested in learning more about Shiny apps")) %>% 
  mutate(Value = c(1)) %>% 
  group_by(N_shiny_users) %>% 
  summarise(Value = sum(Value)) %>% 
  ungroup() %>% 
  mutate(Perc = Value/sum(Value) *100)

dat4 %>% 
  ggplot2::ggplot()+
  ggplot2::geom_col(aes(y = N_shiny_users, x = Perc))+
  ggplot2::ggtitle("Interest in shiny at the center")+
  ggplot2::ylab(element_blank())+
  ggplot2::xlab("Percent of Survey Participants")+
  ecodata::theme_ts()
```

```{r, echo = FALSE, message = FALSE, warning=FALSE}
dat5<- dat2 %>% 
  select(shiny_obstacles) %>% 
  separate(shiny_obstacles, into = c("a", "b", "c", "d"), sep = ",") 

a<- dat5 %>% 
  select(a) %>% 
  rename( "col" = a)
b<- dat5 %>% 
  select(b) %>% 
  rename( "col" = b)
c<- dat5 %>% 
  select(c) %>% 
  rename( "col" = c)
d<- dat5 %>% 
  select(d) %>% 
  rename( "col" = d)

dat5<- rbind(a,b,c,d) %>% 
    filter(!col == "", 
         !col == "NA")%>% 
  mutate(col = recode(col, 
                      "Somewhat more positively: I wish I had time to learn another new thing" = "Time Constraints", 
                      "Don't have time to learn another new thing" = "Time Constraints", 
                      " Don't have time to learn another new thing" = "Time Constraints",
                      " Time constraints are an issue too" = "Time Constraints", 
                      "Don't have the time/full data yet " = "Time Constraints", 
                      " My work needs to be available to collaborators outside of the Center" = "Needs public access", 
                      "My work needs to be available to collaborators outside of the Center" = "Needs public access",
                      " Lack of know how" = "Lack of know how", 
                      " Data confidentiality issues" = "Data confidentiality issues", 
                      "Don't know how to share my app internally on the server" = "Lack of server know how", 
                      " Don't know how to share my app internally on the server" = "Lack of server know how"
                      )) %>% 
  filter(!col == " but would like to try.") %>% 
  dplyr::mutate(Value = c(1)) %>% 
  group_by(col) %>% 
  summarise(Value = sum(Value)) %>% 
  ungroup() %>% 
  mutate(Perc = Value/sum(Value) *100)
dat5 %>% 
  ggplot2::ggplot()+
  ggplot2::geom_col(aes(y = col, x = Perc))+
  ggplot2::ggtitle("Shiny Obstacles")+
  ggplot2::ylab(element_blank())+
  ggplot2::xlab("Percent of Survey Participants")+
  ecodata::theme_ts()

```

```{r}


```

